An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-17 paper/paper.tex
Fit to 8 pages
Add url

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we sort the adversarial samples by ascending distance to the original samples. Then we take samples by ascending distance until we took 50\% of all samples. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged. The resulting average distance is the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more than half of the samples could be made adversarial, our metric is $\infty$ since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Then the ratio of samples that could be made adversarial ($<$50\%) can be a useful metric to determine the exact extent of the adversarial threat. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

>>>>

For reproducibility, we make our code, data and figures publicly available at \url{https://github.com/CN-TU/adversarial-recurrent-ids}.

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we sort the adversarial samples by ascending distance to the original samples. Then we take samples by ascending distance until we took 50\% of all samples. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged, resulting in the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more than half of the samples could be made adversarial, our metric is $\infty$ since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Then the ratio of samples that could be made adversarial ($<$50\%) can be a useful metric to determine the exact extent of the adversarial threat. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
